Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-06 manuscript.tex
edited abstract

{When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density. In particular the strongest correlations have been obtained when using as estimate for the RV the mean of the SN. This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly used parameter to evaluate the asymmetry of the CCF. }
{We strongly encourage the use of the SN density to retrieve the different parameters of the CCF since the correlations used to probe stellar activity are stronger than the ones retrieved by the common approach and because the uncertainties associated to the RV and the asymmetry of the CCF are both smaller than the ones retrieved by the commonly employed strategies.

>>>>

{When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density. 
In particular the strongest correlations have been obtained when using the mean of the SN as an estimate for the RV. 
This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. 
The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly used parameter to evaluate the asymmetry of the CCF. }
{The SN density shape appears to be useful for characterizing the CCF since the correlations used to probe stellar activity are stronger and the uncertainties associated of the estimates for RV and the asymmetry of the CCF are both smaller than those derived from other commonly employed strategies.
